Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-03 manuscript.tex

\begin{tabular}{lllllll}
\toprule
 & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){2-4} \cmidrule(r){5-7}
Metric & Median & Mean & SD & Median & Mean & SD\\
\midrule
Overall Accuracy & 0.913 & 0.852 & 0.145 & 0.926 & 0.917 & 0.074\\
Balanced Accuracy & 0.918 & 0.899 & 0.074 & 0.918 & 0.910 & 0.074\\
F1 & 0.838 & 0.830 & 0.102 & 0.879 & 0.870 & 0.095\\
Sensitivity & 0.859 & 0.840 & 0.122 & 0.856 & 0.846 & 0.125\\
Pos Pred Value & 0.841 & 0.826 & 0.115 & 0.925 & 0.892 & 0.118\\
Kappa & 0.783 & 0.764 & 0.156 & 0.862 & 0.826 & 0.148\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllll}
\toprule
 &  & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){3-5} \cmidrule(r){6-8}
Metric & Position & Median & Mean & SD & Median & Mean & SD\\
\midrule
Balanced Accuracy & Supine & 0.974 & 0.923 & 0.109 & 0.998 & 0.963 & 0.082\\
 & Prone & 0.997 & 0.953 & 0.105 & 0.965 & 0.924 & 0.124\\
 & Sitting & 0.918 & 0.864 & 0.155 & 0.963 & 0.944 & 0.069\\
 & Upright & 0.929 & 0.861 & 0.154 & 0.935 & 0.872 & 0.134\\
 & Held & 0.915 & 0.884 & 0.107 & 0.861 & 0.851 & 0.147\\ \midrule
F1 & Supine & 0.949 & 0.863 & 0.185 & 0.994 & 0.945 & 0.120\\
 & Prone & 0.971 & 0.921 & 0.139 & 0.943 & 0.898 & 0.160\\
 & Sitting & 0.912 & 0.810 & 0.250 & 0.955 & 0.926 & 0.098\\
 & Upright & 0.782 & 0.758 & 0.214 & 0.850 & 0.756 & 0.259\\
 & Held & 0.832 & 0.782 & 0.196 & 0.845 & 0.782 & 0.227\\ \midrule
Sensitivity & Supine & 1.000 & 0.921 & 0.166 & 1.000 & 0.959 & 0.123\\
 & Prone & 1.000 & 0.915 & 0.205 & 0.985 & 0.864 & 0.249\\
 & Sitting & 0.911 & 0.795 & 0.288 & 0.985 & 0.916 & 0.136\\
 & Upright & 0.870 & 0.755 & 0.293 & 0.907 & 0.783 & 0.274\\
 & Held & 0.875 & 0.793 & 0.218 & 0.793 & 0.715 & 0.297\\ \midrule
Pos Pred Value & Supine & 0.993 & 0.814 & 0.300 & 1.000 & 0.941 & 0.127\\
 & Prone & 1.000 & 0.892 & 0.217 & 0.986 & 0.903 & 0.191\\
 & Sitting & 0.926 & 0.841 & 0.242 & 0.974 & 0.947 & 0.071\\
 & Upright & 0.842 & 0.738 & 0.292 & 0.888 & 0.803 & 0.235\\
 & Held & 0.935 & 0.839 & 0.195 & 0.941 & 0.868 & 0.218\\ \midrule
Kappa & Supine & 0.934 & 0.762 & 0.311 & 0.989 & 0.921 & 0.158\\
 & Prone & 0.963 & 0.885 & 0.216 & 0.929 & 0.860 & 0.224\\
 & Sitting & 0.838 & 0.720 & 0.313 & 0.930 & 0.890 & 0.129\\
 & Upright & 0.735 & 0.688 & 0.284 & 0.820 & 0.730 & 0.264\\
 & Held & 0.808 & 0.757 & 0.205 & 0.827 & 0.740 & 0.268\\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lllllll}
\toprule
 & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){2-4} \cmidrule(r){5-7}
Metric & Median & Mean & SD & Median & Mean & SD\\
\midrule
Overall Accuracy & 0.904 & 0.843 & 0.165 & 0.929 & 0.915 & 0.076\\
Balanced Accuracy & 0.923 & 0.898 & 0.077 & 0.918 & 0.909 & 0.072\\
F1 & 0.834 & 0.826 & 0.115 & 0.877 & 0.869 & 0.091\\
Sensitivity & 0.870 & 0.838 & 0.127 & 0.856 & 0.845 & 0.119\\
Pos Pred Value & 0.828 & 0.816 & 0.127 & 0.932 & 0.900 & 0.109\\
Kappa & 0.766 & 0.759 & 0.166 & 0.836 & 0.825 & 0.143\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllll}
\toprule
 &  & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){3-5} \cmidrule(r){6-8}
Metric & Position & Median & Mean & SD & Median & Mean & SD\\
\midrule
Balanced Accuracy & Supine & 0.973 & 0.927 & 0.121 & 0.994 & 0.959 & 0.083\\
 & Prone & 0.997 & 0.949 & 0.112 & 0.978 & 0.924 & 0.126\\
 & Sitting & 0.915 & 0.862 & 0.147 & 0.967 & 0.941 & 0.074\\
 & Upright & 0.934 & 0.867 & 0.153 & 0.933 & 0.879 & 0.120\\
 & Held & 0.903 & 0.876 & 0.114 & 0.864 & 0.842 & 0.155\\ \midrule
F1 & Supine & 0.962 & 0.859 & 0.225 & 0.987 & 0.941 & 0.120\\
 & Prone & 0.972 & 0.911 & 0.164 & 0.943 & 0.894 & 0.171\\
 & Sitting & 0.907 & 0.804 & 0.237 & 0.957 & 0.925 & 0.106\\
 & Upright & 0.818 & 0.772 & 0.217 & 0.864 & 0.771 & 0.234\\
 & Held & 0.841 & 0.793 & 0.164 & 0.839 & 0.764 & 0.241\\ \midrule
Sensitivity & Supine & 1.000 & 0.904 & 0.224 & 1.000 & 0.952 & 0.124\\
 & Prone & 1.000 & 0.906 & 0.219 & 0.985 & 0.865 & 0.254\\
 & Sitting & 0.913 & 0.819 & 0.257 & 0.950 & 0.911 & 0.141\\
 & Upright & 0.880 & 0.765 & 0.291 & 0.883 & 0.798 & 0.243\\
 & Held & 0.864 & 0.780 & 0.235 & 0.789 & 0.698 & 0.315\\ \midrule
Pos Pred Value & Supine & 0.998 & 0.832 & 0.291 & 1.000 & 0.939 & 0.128\\
 & Prone & 1.000 & 0.889 & 0.228 & 0.972 & 0.894 & 0.193\\
 & Sitting & 0.924 & 0.805 & 0.277 & 0.974 & 0.951 & 0.077\\
 & Upright & 0.882 & 0.742 & 0.294 & 0.939 & 0.820 & 0.234\\
 & Held & 0.900 & 0.812 & 0.238 & 0.936 & 0.884 & 0.171\\ \midrule
Kappa & Supine & 0.942 & 0.766 & 0.326 & 0.984 & 0.916 & 0.159\\
 & Prone & 0.962 & 0.875 & 0.236 & 0.933 & 0.855 & 0.232\\
 & Sitting & 0.820 & 0.708 & 0.313 & 0.929 & 0.889 & 0.139\\
 & Upright & 0.773 & 0.701 & 0.291 & 0.804 & 0.743 & 0.242\\
 & Held & 0.809 & 0.743 & 0.220 & 0.826 & 0.721 & 0.279\\
\bottomrule
\end{tabular}
